Evolution of the AGN UV luminosity function from redshift 7.5

### 2017-09-20 Paper/paper.tex
Update text

\title[AGN luminosity function]{Evolution of the AGN UV luminosity function}

@@

\begin{abstract}
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur
  eget nisi augue. Vivamus quis purus quis massa tempor posuere non
  quis magna. Aenean eleifend, metus eget facilisis faucibus, turpis
  erat suscipit tortor, ut dapibus nulla neque ac sapien. Suspendisse
  luctus eros eu quam laoreet, vel dapibus sem porttitor. Mauris nec
  massa ultrices, porttitor nulla at, euismod diam. In ultricies
  malesuada mauris ac facilisis. Nulla quis suscipit diam, vitae
  semper tortor. Proin nec nulla at massa egestas porta. Cras ac arcu
  in velit placerat facilisis fringilla in sem. Mauris finibus, mauris
  ut pretium malesuada, massa urna mattis nibh, at placerat ligula
  elit ac odio.  Nunc vel leo arcu. Nullam sagittis tincidunt
  interdum. Mauris sed lacus cursus, dapibus enim non, sagittis
  leo. Aliquam sit amet ex ut quam iaculis sollicitudin. Vivamus ut
  pharetra dolor. Vivamus id nibh leo. Vestibulum consectetur eu lorem
  eu tincidunt. Sed eget nibh orci. Pellentesque sit amet blandit
  massa, vel tempor neque.
\end{abstract}

\begin{keywords}
quasars
\end{keywords}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
  \end{center}
  \caption{AGN number density evolution in the global model.}
  \label{fig:rhoqso}
\end{figure}

@@

@@

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
    \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
    \end{tabular}
  \end{center}
  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
    Model luminosity functions are integrated down to $M_{1450}=-18$
    in the left panel and $-20$ in the right panel.}
  \label{fig:gammapi}
\end{figure*}

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur
eget nisi augue. Vivamus quis purus quis massa tempor posuere non quis
magna. Aenean eleifend, metus eget facilisis faucibus, turpis erat
suscipit tortor, ut dapibus nulla neque ac sapien. Suspendisse luctus
eros eu quam laoreet, vel dapibus sem porttitor. Mauris nec massa
ultrices, porttitor nulla at, euismod diam. In ultricies

>>>>

\title[AGN luminosity function]{Evolution of the AGN UV luminosity function from redshift 7.5}

@@

\begin{abstract}
We present the evolution UV/optical luminosity function of quasars
from a homogeneous reanalysis of more than 85,000 spectroscopically
selected quasars from redshift $z=0$ to $7.5$.  We derived luminosity
functions when the observed quasar population is binned in luminosity
and redshift, and then construct a continuous evolutionary model of
the luminosity function spanning a range of redshifts.  We find that
quasars selected from the BOSS survey at $z=2$--$3$ show a significant
systematic offset from the general trends, possiblity due to the
colour bias suffered by BOSS.  Some systematic errors also persist in
the lowest-redshift quasar sample due to host galaxy effects. However,
we find that it is possible to describe the luminosity function
evolution from redshift $z=0$ to $7.5$ using a simple 14-parameter
evolving double power law model.  The evolution of the number density
of qsos shows the familiar downsizing effect, although the evolution
in the faint quasar population is quite flat at high redshifts such
that the the drop in their number density at high redshifts is much
slower than that for bright quasars.  When integrated down to
$M_{1450}=-20$ quasars can produce all of the hydrogen-ionizing
photons in the intergalactic medium upto redshifts 3.5.  They fall
short of the emissivity required to explain the Ly$\alpha$ data at
higher redshifts, and are therefore unlikely to have singlehandedly
driven hydrogen reionization.  This conclusion can be altered,
however, if lower luminosity qsos (down to $M_{1450}=-18$) are assumed
to exist and to have a unity escape fraction, in which case qsos can
potentially produce all the hydrogen-ionizing flux at $z<7.5$.
He~\textsc{ii} reionization in this model occurs between $z=3.2$ and
$3.7$.
\end{abstract}

\begin{keywords}
dark ages, reionization, firs stars -- intergalactic medium -- quasars: general -- galaxies: active 
\end{keywords}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
  \end{center}
  \caption{AGN number density evolution in the global model.  Similar
    to Figure~\ref{fig:evoln_global}, symbols show the best fit
    parameters with 68\% uncertainties from the double power law fits
    to the data in redshift bins.  Black solid curve shows the best
    fit global model, and the coloured curves show a random sample
    drawn from the global posterior.  \textbf{[Show rejected bins in
        differnt symbols here.  Do not show the $-18$ case.  Cut the
        figure off at 6.5.]}}
  \label{fig:rhoqso}
\end{figure}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
    \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
    \end{tabular}
  \end{center}
  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
    Model luminosity functions are integrated down to $M_{1450}=-18$
    in the left panel and $-20$ in the right panel.}
  \label{fig:e912}
\end{figure*}

@@

The evolution of the comoving number density of quasars is shown in
Figure~\ref{fig:rhoqso} when the luminosity function is integrated
down to different limits.  Similar to Figure~\ref{fig:evoln_global},
symbols show the best fit parameters with 68\% uncertainties from the
double power law fits to the data in redshift bins.  Black solid curve
shows the best fit global model, and the coloured curves show a random
sample drawn from the global posterior.  Bins with BOSS qsos are not
shown.  The number density of qsos down to the limit of spectroscopic
data is about 1 per $10^5$ cMpc$^3$ at its peak.  This density rapidly
increases at low redshifts and then drops gradually at high redshifts.
Figure~\ref{fig:rhoqso} also shows the familiar downsizing feature in
which the number density of faint qsos peaks are lower redshifts than
that of the bright qsos.  While the number density of qsos with
$M_*<-27$ peaks at $z\sim 2.5$, the number density of qsos with
$M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at which
spectroscopic data exist, $M_*<-21$, the number density of qsos peaks
at $z\sim 1$.

@@

%% \begin{figure*}
%%   \begin{center}
%%     \begin{tabular}{cc}
%%     \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
%%     \includegraphics[width=0.5\textwidth]{emissivity_20.pdf}
%%     \end{tabular}
%%   \end{center}
%%   \caption{LyC emissivity of AGN assuming 100\% escape fraction.
%%     Model luminosity functions are integrated down to $M_{1450}=-18$
%%     in the left panel and $-20$ in the right panel.}
%%   \label{fig:gammapi}
%% \end{figure*}

@@

% Check spellings
% Check notes for more names with add
% Something to add for Joe and Gabor?
We acknowledge useful discussions with James Aird, Manda Banerji,
Tirthankar Roy Choudhury, Xiaohui Fan, Andrea Ferrara, Martin
Haehnelt, Sergey Koposov, Richard McMahon, Ewald Puchwein, Gordon
Richards, and Alberto Rorai for helpful discussions.  GK is supported
by ERC Advanced Grant 320596 `The Emergence of Structure During the
Epoch of Reionization'.
